Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Structure

### 2017-04-06 documents/TriangleScenarioArXiv/ts.tex
removed the appendix for parameterizations, now included in the main body and much shorter

\begin{document}
    \title{Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Structure}
    \author{Thomas C. Fraser}
    \email{tcfraser@tcfraser.com}
    \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada, N2L 2Y5}
    \affiliation{University of Waterloo, Waterloo, Ontario, Canada, N2L 3G1}
    \author{Elie Wolfe}
    \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada, N2L 2Y5}
    % \email{ewolfe@perimeterinstitute.ca}
    \date{\today}
    \begin{abstract}
        It has long been recognized that certain quantum correlations are often incompatible with particular assumption about classical causal structure. Such correlations are sometimes termed non-local, although they are more accurately termed non-classical, as the presence of correlations certifies the genuinely non-classical nature of a causal setup in a device-independent fashion.  Whenever a quantum correlation violates a causal compatibility inequality (e.g. a Bell inequality) then the correlation is witnessed as non-classical. Any constraint which is satisfied by all correlations which \textit{are} classically compatible with a given causal structure defines a causal compatibility criterion. Such criteria were recently were recently derived for the Triangle structure [\href[pdfnewwindow]{http://arxiv.org/abs/1609.00672}{arXiv:1609.00672}] in the form of polynomial inequalities, begging the question: do any of those inequalities admit violation by quantum correlations? Numerical investigation suggests not, and we further conjecture that the set of correlations admitted by the classical Triangle structure is equivalent to the set of correlations admitted by its quantum generalization whenever the three observable variables are binary. Our main contribution in this work, however, is the derivation of new causal compatibility inequalities for the Triangle structure which \textit{do} admit quantum violation. We conclude by considering the possibility of quantum resources potentially qualitatively different from those known previously.
    \end{abstract}
    \maketitle
    \tableofcontents
    % \setlength{\parskip}{1em}
    \clearpage

@@

    \term{Fritz's Problem}: Find an example of non-classical quantum correlations in the Triangle structure together with a proof of its non-classicality which does not hinge on Bell’s theorem.\footnote{In the way Fritz defines, \textit{non-classical} correlations are the class of \textit{incompatible} correlations.}

@@

    \section{Noisy Distributions \& Numerical Optimizations}
    \label{sec:violations_noise}
    Causal compatibility inequalities for the Triangle structure (such as those derived in \cref{sec:deriving_inequalities}) offer an avenue into studying quantum non-classicality. In this section, we make use of two methods, exposure to noise and numerical optimization, to further understand the nature of quantum non-classicality in connection to compatibility inequalities.

@@

    For Triangle structure, we define a completely noisy observation as the uniform probability distribution $\s{U}\br{abc} = \s{U}_{ABC}\br{abc} = \f{1}{64} \quad \forall a,b,c\in \bc{0,1,2,3}$ (see \cref{fig:uniform_distribution}). Since the uniform distribution $\s{U}$ is trivially compatible with the Triangle structure, the objective of this section is to determine how much uniform noise needs to be added to the Fritz distribution $\prob[\fritz]$ before it transitions from incompatible to compatible. We do this by defining an affine noise parameter $\vep$ such that $0 \leq \vep \leq 1$ along with the \term{noisy variant} $\s{N}_{\vep}$ of the Fritz distribution,
    \[ \s{N}_{\vep} = \br{1 - \vep} \prob[\fritz] + \vep \s{U} \]
    Therefore as $\vep$ varies from $0$ to $1$, more and more noise is added to the Fritz distribution and $\s{N}_{\vep}$ transitions from an incompatible distribution $\s{N}_{0} = \prob[\fritz]$ to a compatible distribution $\s{N}_{1} = \s{U}$. For each inequality $I$ and distribution $\prob$, let $I\br{\prob}$ denote a scalar value representing the amount of violation seen by $\prob$. In order to compare different inequalities simultaneously, let $I\br{\prob} < 0$ represent a violation of $I$ while $I\br{\prob} \leq 0$ represents satisfaction of $I$ (with $I\br{\prob} = 0$ corresponding to complete saturation of the inequality). To analyze noise, $4$ inequalities where chosen. First, $I_0$ is the inequality derived using the Wagon-Wheel wheel inflation \cref{eq:ww_ineq}. The other three inequalities $I_1, I_2, I_3$ were all derived using the Web inflation; $I_1$ can be found in \cref{sec:web_inequality} while $I_3$ is the symmetric inequality in \cref{sec:symmetic_web_inequality}. Inequality $I_2$ is not reproduced anywhere in this document but is similar to \cref{sec:web_inequality}. Our tests suggest that inequality $I_1$ (\cref{sec:web_inequality}) is most robust to noise and demonstrates that the Fritz distribution remains incompatible with the Triangle structure up to at least a noise parameter of $\vep \simeq 0.085$. The associated distribution $\s N_{0.085}\br{\prob[\fritz]}$ is plotted in \cref{fig:noisy_fritz}. Of course, there remains the possibility that another inequality will be able to withstand a larger degree of noise than $I_1$.

@@

    \subsection{Numerical Optimizations}
    \label{sec:optimizations}
    Causal compatibility inequalities act as a \textit{measure} of non-classicality. If two non-classical distributions $\prob[1]$ and $\prob[2]$ violate the same inequality $I$ with violations $I\br{\prob[1]}$ and $I\br{\prob[2]}$ respectively, it is somewhat reasonable to say that $\prob[1]$ is \textit{more} non-classical than $\prob[2]$ whenever ${I\br{\prob[1]}} < I\br{\prob[2]}$\footnote{Remember that larger violations are more negative when the inequalities are written in the proposed canonical form.} Nonetheless, this statement comes from several caveats. First, it is possible (and frequently the case) for ${I\br{\prob[1]}} < I\br{\prob[2]}$ to hold for one inequality $I$ but have ${\ti I\br{\prob[2]}} < \ti I\br{\prob[1]}$ hold for another inequality $\ti I$. In this case, all one can claim is that $\prob[1]$ is more incompatible than $\prob[2]$ with respective to $I$ but the contrary is true with respect to $\ti I$. Second, not all inequalities $I$ are \textit{good} measures of non-classicality. In the case of the Bell structure, the linear inequality constraints associated with the facets of the marginal polytope are the best measures of non-classicality. This is because the facets form a necessary and sufficient set with all other inequalities following from positive mixtures of the facets. However, good measures of incompatibility are less understood in the Triangle structure where the space of classical correlations is non-convex. At the very least, the inequalities derived in this report are likely \textit{not} the best measures of incompatibility (especially because they are curated toward the Fritz distribution). Nonetheless, these inequalities act the \textit{first} measures of non-classicality in the Triangle structure.

    In order to find quantum distributions that are more non-classical than the Fritz, we performed numerical optimizations against a objective scalar function $f: \R^n \in \R$ using the following pipeline: To begin, a set of real-valued parameters $\la = \br{\la_0, \ldots, \la_n} \in \R^{n}$ are used to parameterize a set of quantum states $\rho_{AB}, \rho_{BC}, \rho_{CA}$ and measurements $M_A, M_B, M_C$ in agreement with the quantum version of the Triangle structure in \cref{fig:triangle_structure_quantum_model}. Second, a $4$-outcome distribution $\prob[ABC]$ is obtained via \cref{eq:quantum_model_triangle} and supplanted into an inequality $I$ in homogeneous and canonical form $I\br{\prob[ABC]} \leq 0$. The objective value is simply the degree of violation $f = I\br{\prob[ABC]}$ and used to make adjustments to $\la$ in order to achieve largest and larger violations.

    Finding larger violations to compatibility inequalities is nothing more that a numerical optimization (specifically minimization) of $f\br{\la}$. Since the inequalities themselves are polynomial and the space of quantum-accessible distributions is non-convex, a number of optimization methods were used in an attempt to eliminate any issues associated with local minima or ill-conditioned convergence. Specifically, the BFGS method~\cite[p. 142]{Nocedal_2000} and the Nelder-Mead simplex method~\cite[p. 238]{Nocedal_2000} were used along with a method called Basin Hopping~\cite{Wales_1997}, which is a hybrid between simulated annealing and gradient descent-based methods.

    % \subsection{Parameterizing Quantum Distributions}
    \begin{figure}
    \begin{center}
            \scalebox{1.0}{\input{../../figures/causal_structures/triangle_structure_operational}}
            \caption{The Triangle structure as modeled by quantum states and measurements.}
            \label{fig:triangle_structure_quantum_model}
    \end{center}
    \end{figure}
    In search of new, incompatible, quantum distributions that can be realized on the Triangle structure, numerical optimizations over the the space of quantum-accessible probability distributions are performed. To do so, we are interested in a parameterization all distributions that can be expressed as follows:
    \[ \prob[\p{ABC}]\br{abc} = \Tr\bs{\netperm^\intercal \rho_{\p{AB}}\otimes\rho_{\p{BC}}\otimes\rho_{\p{CA}} \netperm M_{\p{A},a}\otimes M_{\p{B},b} \otimes M_{\p{C},c}} \eq \label{eq:quantum_model_triangle}\]
    Where $\rho_{\p{AB}}, \rho_{\p{BC}}, \rho_{\p{CA}}$ are bipartite density matrices, $M_{\p{A}}, M_{\p{B}}, M_{\p{C}}$ are generic measurements sets and $\netperm$ is a permutation matrix that aligns the states and measurements appropriately\footnote{$\netperm$ is discussed more thoroughly in \cref{sec:perm_matrix}.}.

    In order to qualify the scope of \cref{eq:quantum_model_triangle} and associated computational complexity of the parameterization, there are a two restrictions that are made with justification. The states $\rho$ are taken to be bipartite \textit{qubit} states acting on $\s{H}^{2} \otimes \s{H}^{2}$. This is motivated by \cref{sec:fritz_distribution} in which the Fritz distribution only requires qubit states. In generality, one could consider $n$-dimensional states acting on $\s{H}^{n} \otimes \s{H}^{n}$. However, in such cases the joint density matrix $\rho_{\p{AB}}\otimes\rho_{\p{BC}}\otimes\rho_{\p{CA}}$ then acts on $\br{\Hilb^{n}}^{\otimes 6}$ requiring a $n^6 \times n^6$ matrix with $n^{12}$ entries. Therefore, $n = 2$ is far more computationally feasible than $n > 2$. Additionally, restrict our focus to projective-valued measures (PVMs) instead of projective-operator valued measures (POVMs) for three reasons. First, \cref{sec:fritz_distribution} demonstrates that PVMs are sufficient for witnessing incompatible quantum distributions in the Triangle structure. Second, generating $k$-outcome POVM measurements is possible using rejection sampling techniques~\cite{Petz_2015}, however a valid, unbiased parameterization was not found for $k > 2$. Finally, PVMs provide considerable computational advantage over POVMs as they permit \cref{eq:quantum_model_triangle} to be re-written as follows:
    \[ \prob[\p{ABC}]\br{abc} = \bramidket{m_{\p{A},a}m_{\p{B},b}m_{\p{C},c}}{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm}{m_{\p{A},a}m_{\p{B},b}m_{\p{C},c}} \eq \label{eq:quantum_model_triangle_pvms}\]

    In order to parameterize all such distributions, we elect to parameterize the states and measurements separately. Although there are numerous techniques that can used when parameterizing quantum states and measurements~\cite{Petz_2015, Hedemann_2013,Fujii_2005,James_2001,Grasmair_2014,Neilsen_Chaung_2011}, although a single technique is presented in \cref{sec:unitary_group} that was found to be most computationally suitable for our purposes. \Cref{sec:param_quantum_dist} expounds on our parameterized of the space of quantum distributions that can be realized on the quantum Triangle structure (\cref{fig:triangle_structure_quantum_model}) pursuant to \cref{eq:quantum_model_triangle_pvms}. Specifically, each bipartite quantum resource is modeled $2$-qubit, $4\times 4$ density matrix and each measurement is modeled as a $4$-element projective-value measure.

@@

    \clearpage
    \appendix

@@

    \clearpage
    \section{Quantum Parameterization of Triangle Structure}
    \label{sec:param_quantum_dist}
    \subsection{Unitary Group}
    \label{sec:unitary_group}
    To facilitate the parameterization of quantum states states and PVMs, a parameterization of the unitary group of dimension $d$ (denoted $\s{U}\br{d}$) by Spengler, Huber and Hiesmayr~\cite{Spengler_2010_Unitary} is introduced. Discussions of its application to states and measurements are deferred to \cref{sec:states} and \cref{sec:measurements} respectively.

    In Ref.~\cite{Spengler_2010_Unitary}, Spengler \textit{et al.} proved that all unitaries $U \in \s{U}\br{d}$ can be parameterized without degeneracy as follows:
    \[ U = \bs{\prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} \exp\br{i P_n \lambda_{n,m}}\exp\br{i \si_{m,n} \lambda_{m,n}}}} \cdot \bs{\prod_{l=1}^{d} \exp\br{iP_l \lambda_{l,l}}}  \eq \label{eq:spengler_unitary} \]
    Where $\la = \bc{\la_{n,m} \mid n,m \in 1, \ldots, d}$ form a $d \times d$ matrix of real-valued parameters with periodicities $\la_{m,n} \in \bs{0, \f{\pi}{2}}$ for $m < n$ and $\la_{m,n} \in \bs{0, 2 \pi}$ for $m \geq n$.
    \[ \la = \begin{pmatrix}
        \la_{1,1} & \cdots & \la_{1, d} \\
        \vdots & \ddots & \vdots \\
        \la_{d,1} & \cdots & \la_{d, d} \\
    \end{pmatrix} \]
    And where $P_l$ are one-dimensional projective operators,
    \[ P_l = \ket{l}\bra{l} \qquad 1 \leq l \leq d \eq \label{eq:projective_operator} \]
    and the $\si_{m,n}$ are generalized anti-symmetric $\si$-matrices,
    \[ \sigma_{m,n} = -i \ket{m}\bra{n} +i \ket{n}\bra{m} \qquad 1 \leq m < n \leq d\]
    The SSH parameterization (\cref{eq:spengler_unitary}) is unique in that each of the real-valued parameters $\la_{n,m}$ has physical significance. For the sake of reference, let us label the matrix exponential terms in \cref{eq:spengler_unitary} in a manner that corresponds to their affect on an orthonormal basis $\bc{\ket{1}, \ldots, \ket{d}}$.
        GP_l &= \exp\br{iP_l \lambda_{l,l}} \\
        RP_{n,m} &= \exp\br{i P_n \lambda_{n,m}} \\
        R_{m,n} &= \exp\br{i \si_{m,n} \lambda_{m,n}}
    \end{split} \eq \label{eq:exp_terms}
    For example, $R_{m,n} = \exp\br{i \si_{m,n} \lambda_{m,n}}$ applies a rotation to the sub-space spanned by $\ket{m}$ and $\ket{n}$ for $m < n$. Analogously, $RP_{n,m}$ generates the relative phase between $\ket{m}$ and $\ket{n}$ for $m > n$ and $GP_l$ fixes the global phase of $\ket{l}$. Possessing a parameterization that maintains this physical interpretation is useful as it allows one to readily eliminate any degeneracies. For the purposes of quantum distributions such as \cref{eq:quantum_model_triangle}, it should be clear that any contributions to global phase are irrelevant. The SSH parameterization becomes especially attractive because it readily permits one to drop the global phase terms by setting $\la_{l,l} = 0$ for all $l = 1, \ldots, d$. It is convenient to denote the set of all unitaries up to global phase considerations as $\ti {\s{U}}\br{d}$ and express $\ti {U} \in \ti {\s{U}}\br{d}$ using $d\br{d-1}$ real-valued parameters:
    \[ \ti U = \prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} RP_{n,m}R_{m,n}} \eq \label{eq:spengler_unitary_gp} \]
    Another attractive feature of the SSH parameterization not mentioned in~\cite{Spengler_2010_Unitary} is that \cref{eq:spengler_unitary}, and thus \cref{eq:spengler_unitary_gp}, can be implemented in a computationally efficient manner. This is discussed in \cref{sec:comp_spengler}.
    \subsection{Measurements}
    \label{sec:measurements}
    For each measurement set $M$ in \cref{eq:quantum_model_triangle}, we consider a $d$-element projective-valued measure (PVM) $M = \bc{M_1, \ldots, M_d}$ satisfying a number of familiar constraints:
    \begin{gather*}

>>>>

\begin{document}
    \title{Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Structure}
    \author{Thomas C. Fraser}
    \email{tcfraser@tcfraser.com}
    \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada, N2L 2Y5}
    \affiliation{University of Waterloo, Waterloo, Ontario, Canada, N2L 3G1}
    \author{Elie Wolfe}
    \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada, N2L 2Y5}
    % \email{ewolfe@perimeterinstitute.ca}
    \date{\today}
    \begin{abstract}
        It has long been recognized that certain quantum correlations are often incompatible with particular assumption about classical causal structure. Such correlations are sometimes termed non-local, although they are more accurately termed non-classical, as the presence of correlations certifies the genuinely non-classical nature of a causal setup in a device-independent fashion.  Whenever a quantum correlation violates a causal compatibility inequality (e.g. a Bell inequality) then the correlation is witnessed as non-classical. Any constraint which is satisfied by all correlations which \textit{are} classically compatible with a given causal structure defines a causal compatibility criterion. Such criteria were recently were recently derived for the Triangle structure [\href[pdfnewwindow]{http://arxiv.org/abs/1609.00672}{arXiv:1609.00672}] in the form of polynomial inequalities, begging the question: do any of those inequalities admit violation by quantum correlations? Numerical investigation suggests not, and we further conjecture that the set of correlations admitted by the classical Triangle structure is equivalent to the set of correlations admitted by its quantum generalization whenever the three observable variables are binary. Our main contribution in this work, however, is the derivation of new causal compatibility inequalities for the Triangle structure which \textit{do} admit quantum violation. We conclude by considering the possibility of quantum resources potentially qualitatively different from those known previously.
    \end{abstract}
    \maketitle
    \tableofcontents
    % \setlength{\parskip}{1em}

@@

    \term{Fritz's Problem}: Find an example of non-classical quantum correlations in the Triangle structure together with a proof of its non-classicality which does not hinge on Bell’s theorem.

@@

    \section{Numerical Optimizations \& Noisy Distributions}
    \label{sec:violations_noise}
    Causal compatibility inequalities for the Triangle structure (such as those derived in \cref{sec:deriving_inequalities}) offer an avenue into studying quantum non-classicality. In this section, we make use of two methods, exposure to noise and numerical optimization, to further understand the nature of quantum non-classicality in connection to compatibility inequalities. In order to compare different inequalities simultaneously, our convention is to rearrange each inequality $I$ so $I\br{\prob} < 0$ represent a violation of $I$ while $I\br{\prob} \leq 0$ represents satisfaction of $I$ (with $I\br{\prob} = 0$ corresponding to complete saturation of the inequality). For the subsequent analysis, $4$ inequalities where chosen. First, $I_0$ is the inequality derived using the Wagon-Wheel wheel inflation \cref{eq:ww_ineq}. The other three inequalities $I_1, I_2, I_3$ were all derived using the Web inflation; $I_1$ can be found in \cref{sec:web_inequality} while $I_3$ is the symmetric inequality in \cref{sec:symmetic_web_inequality}. Inequality $I_2$ is not reproduced anywhere in this document but is similar to \cref{sec:web_inequality}.

@@

    For Triangle structure, we define a completely noisy observation as the uniform probability distribution $\s{U}\br{abc} = \s{U}_{ABC}\br{abc} = \f{1}{64} \quad \forall a,b,c\in \bc{0,1,2,3}$ (see \cref{fig:uniform_distribution}). Since the uniform distribution $\s{U}$ is trivially compatible with the Triangle structure, the objective of this section is to determine how much uniform noise needs to be added to the Fritz distribution $\prob[\fritz]$ before it transitions from incompatible to compatible. We do this by defining an affine noise parameter $\vep$ such that $0 \leq \vep \leq 1$ along with the \term{noisy variant} $\s{N}_{\vep}$ of the Fritz distribution,
    \[ \s{N}_{\vep} = \br{1 - \vep} \prob[\fritz] + \vep \s{U} \]
    Therefore as $\vep$ varies from $0$ to $1$, more and more noise is added to the Fritz distribution and $\s{N}_{\vep}$ transitions from an incompatible distribution $\s{N}_{0} = \prob[\fritz]$ to a compatible distribution $\s{N}_{1} = \s{U}$. For each inequality $I$ and distribution $\prob$, let $I\br{\prob}$ denote a scalar value representing the amount of violation seen by $\prob$.  Our tests suggest that inequality $I_1$ (\cref{sec:web_inequality}) is most robust to noise and demonstrates that the Fritz distribution remains incompatible with the Triangle structure up to at least a noise parameter of $\vep \simeq 0.085$. The associated distribution $\s N_{0.085}$ is plotted in \cref{fig:noisy_fritz}. Of course, there remains the possibility that another inequality will be able to withstand a larger degree of noise than $I_1$.

@@

    \subsection{Numerical Optimizations}
    \label{sec:optimizations}
    Causal compatibility inequalities act as a \textit{measure} of non-classicality. If two non-classical distributions $\prob[1]$ and $\prob[2]$ violate the same inequality $I$ with violations $I\br{\prob[1]}$ and $I\br{\prob[2]}$ respectively, it is somewhat reasonable to say that $\prob[1]$ is \textit{more} non-classical than $\prob[2]$ whenever ${I\br{\prob[1]}} < I\br{\prob[2]}$. However, this statement is accompanied by a few caveats. First, it is possible (and frequently the case) for ${I\br{\prob[1]}} < I\br{\prob[2]}$ to hold for one inequality $I$ but have ${\ti I\br{\prob[2]}} < \ti I\br{\prob[1]}$ hold for another inequality $\ti I$. In this case, all one can claim is that $\prob[1]$ is more incompatible than $\prob[2]$ with respective to $I$ but the contrary is true with respect to $\ti I$. Second, not all inequalities $I$ are \textit{good} measures of non-classicality. In the case of the Bell structure, the linear inequality constraints associated with the facets of the marginal polytope are the best measures of non-classicality because the facets form a necessary and sufficient of constraints with all other inequalities following from positive mixtures. However, good measures of incompatibility are less understood in the Triangle structure where the space of classical correlations is non-convex. At the very least, the inequalities derived in this report are likely \textit{not} the best measures of incompatibility simply because they have be curated toward the Fritz distribution. Nonetheless, these inequalities act the \textit{first} measures of non-classicality in the Triangle structure.

    In order to find quantum distributions that are more non-classical than the Fritz, we performed numerical optimizations against each inequality $I$ by parameterizing the space of quantum-accessible probability distributions that can be expressed as follows:
    \[ \prob[\p{ABC}]\br{abc} = \Tr\bs{\netperm^\intercal \rho_{\p{AB}}\otimes\rho_{\p{BC}}\otimes\rho_{\p{CA}} \netperm M_{\p{A},a}\otimes M_{\p{B},b} \otimes M_{\p{C},c}} \eq \label{eq:quantum_model_triangle}\]
    Where $\rho_{\p{AB}}, \rho_{\p{BC}}, \rho_{\p{CA}}$ are bipartite density matrices, $M_{\p{A}}, M_{\p{B}}, M_{\p{C}}$ are generic measurements sets and $\netperm$ is a permutation matrix that aligns the states and measurements appropriately. In order to parameterize all such distributions, we elect to parameterize the states and measurements separately. In order to qualify the scope of \cref{eq:quantum_model_triangle} and associated computational complexity of the parameterization, there are a two restrictions that are made with justification. Motivated by the fact that the Fritz distribution (\cref{sec:fritz_distribution}) only requires qubit states, the states $\rho$ are taken to be bipartite \textit{qubit} states. Qubit states are more computationally feasible compared to $n$-dimensional states whereby the joint density matrix $\rho_{\p{AB}}\otimes\rho_{\p{BC}}\otimes\rho_{\p{CA}}$ becomes an $n^6 \times n^6$ matrix. Additionally, we restrict our focus to projective-valued measures (PVMs) instead of projective-operator valued measures (POVMs) for three reasons. First, \cref{sec:fritz_distribution} demonstrates that PVMs are sufficient for witnessing incompatible quantum distributions in the Triangle structure. Second, although generating $k$-outcome POVM measurements is possible using rejection sampling techniques~\cite{Petz_2015}, a valid, unbiased parameterization was not found for $k > 2$. Finally, PVMs provide considerable computational advantage over POVMs as they permit \cref{eq:quantum_model_triangle} to be re-written as \cref{eq:quantum_model_triangle_pvms}.
    \[ \prob[\p{ABC}]\br{abc} = \bramidket{m_{\p{A},a}m_{\p{B},b}m_{\p{C},c}}{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm}{m_{\p{A},a}m_{\p{B},b}m_{\p{C},c}} \eq \label{eq:quantum_model_triangle_pvms}\]

    Although there are numerous techniques that can used when parameterizing quantum states and measurements~\cite{Petz_2015, Hedemann_2013,Fujii_2005,James_2001,Grasmair_2014,Neilsen_Chaung_2011}, a single technique by \citet{Spengler_2010_Unitary} was found to be most computationally suitable for our purposes. \Citet{Spengler_2010_Unitary} demonstrated that all $d\times d$ unitary matrices $U$ can be parameterized without degeneracy as follows:
    \[ U = \bs{\prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} \exp\br{i P_n \lambda_{n,m}}\exp\br{i \si_{m,n} \lambda_{m,n}}}} \cdot \bs{\prod_{l=1}^{d} \exp\br{iP_l \lambda_{l,l}}}  \eq \label{eq:spengler_unitary} \]
    Where the real valued parameters $\la = \bc{\la_{n,m} \mid n,m \in 1, \ldots, d}$ have periodicities $\la_{m,n} \in \bs{0, \f{\pi}{2}}$ for $m < n$ and $\la_{m,n} \in \bs{0, 2 \pi}$ for $m \geq n$. Moreover, $P_l$ are one-dimensional projective operators $P_l = \ket{l}\bra{l}$ and the $\si_{m,n}$ are generalized anti-symmetric $\si$-matrices $\sigma_{m,n} = -i \ket{m}\bra{n} +i \ket{n}\bra{m}$ where $1 \leq m < n \leq d$. This parameterization has the useful feature that each of the real-valued parameters $\la_{n,m}$ a direct and intuitive physical affect on each element of a computational basis $\bc{\ket{1}, \ldots, \ket{d}}$. Explicitly, $\exp\br{i \si_{m,n} \lambda_{m,n}}$ applies a rotation to the sub-space spanned by $\ket{m}$ and $\ket{n}$ for $m < n$. Analogously, $\exp\br{i P_n \lambda_{n,m}}$ generates the relative phase between $\ket{m}$ and $\ket{n}$ for $m > n$ and $\exp\br{iP_l \lambda_{l,l}}$ fixes the global phase of $\ket{l}$. Finally, although not explicitly mentioned in~\cite{Spengler_2010_Unitary}, it is possible to remove the reliance on the computationally expensive matrix exponential operations in \cref{eq:spengler_unitary}~\cite{Moler_2003}.

    By parameterizing unitary matrices, it becomes possible to parameterize $d$-dimensional density matrices and $d$-element PVMs by recognizing that any orthonormal basis $\bc{\ket{\psi_j}}$ (where $1 \leq j \leq d$) can be transformed into the computational basis $\bc{\ket{j}}$ by a unitary transformation $U$, i.e. $U \ket{\psi_j} = \ket{j}$. First consider a $d$-element PVM $M = \bc{\ket{m_j}\bra{m_j} \mid 1 \leq j \leq d}$. Since $\bc{\ket{m_j}}$ forms an orthonormal basis, one can parameterize $M$ by writing $M = \bc{U^{\dagger}\ket{j}\bra{j}U \mid 1 \leq j \leq d}$ and parameterizing $U$ using \cref{eq:spengler_unitary}. This method was inspired by the measurement seeding method for iterative optimization used by \citet{Pal_2010}. Analogously, this argument can be extended to full-rank $d$-dimensional density matrices $\rho$ by performing a spectral decomposition $\rho = \sum_{j=1}^{d} p_j \ket{p_j} \bra{p_j}$ into eigenvalues $\bc{p_j}$ and eigenstates $\bc{\ket{p_j}}$. Since $\Tr\bc{\rho} = \sum_{j = 1}^{d} p_j = 1$ the eigenvalues of $\rho$ are parameterized without degeneracy using a tuple of $d-1$ real-valued parameters with periodicity $\bs{0, 2 \pi}$ using hyper-spherical coordinates~\cite{Hedemann_2013, Spengler_2010_Unitary}. Additionally, since $\rho$ is Hermitian, the eigenstates $\bc{\ket{p_j}}$ form an orthonormal basis and therefore the eigenstates are analogously parameterized using \cref{eq:spengler_unitary}: $\rho = \sum_{j=1}^{d} p_j U^{\dagger} \ket{j} \bra{j} U$. For our purposes, we have set $d = 4$ and fixed $\la_{l, l} = 0$ for $1 \leq l \leq d$ in \cref{eq:spengler_unitary} because the global phase contributions are irrelevant in \cref{eq:quantum_model_triangle_pvms}.
    \[  \]
    % \Cref{sec:param_quantum_dist} expounds on our parameterized of the space of quantum distributions that can be realized on the quantum Triangle structure (\cref{fig:triangle_structure_quantum_model}) pursuant to \cref{eq:quantum_model_triangle_pvms}. Specifically, each bipartite quantum resource is modeled $2$-qubit, $4\times 4$ density matrix and each measurement is modeled as a $4$-element projective-value measure.

    % the a objective scalar function $f: \R^n \in \R$ using the following pipeline: To begin, a set of real-valued parameters $\la = \br{\la_0, \ldots, \la_n} \in \R^{n}$ are used to parameterize a set of quantum states $\rho_{AB}, \rho_{BC}, \rho_{CA}$ and measurements $M_A, M_B, M_C$ in agreement with the quantum version of the Triangle structure in \cref{fig:triangle_structure_quantum_model}. Second, a $4$-outcome distribution $\prob[ABC]$ is obtained via \cref{eq:quantum_model_triangle} and supplanted into an inequality $I$ in homogeneous and canonical form $I\br{\prob[ABC]} \leq 0$. The objective value is simply the degree of violation $f = I\br{\prob[ABC]}$ and used to make adjustments to $\la$ in order to achieve largest and larger violations.

    Since the inequalities themselves are polynomial and the space of quantum-accessible distributions is non-convex, a number of optimization methods were used in an attempt to eliminate any issues associated with local minima or ill-conditioned convergence. Specifically, the BFGS method~\cite[p. 142]{Nocedal_2000} and the Nelder-Mead simplex method~\cite[p. 238]{Nocedal_2000} were used along with a method called Basin Hopping~\cite{Wales_1997}, which is a hybrid between simulated annealing and gradient descent-based methods.

    % \subsection{Parameterizing Quantum Distributions}
    \begin{figure}
    \begin{center}
            \scalebox{1.0}{\input{../../figures/causal_structures/triangle_structure_operational}}
            \caption{The Triangle structure as modeled by quantum states and measurements.}
            \label{fig:triangle_structure_quantum_model}
    \end{center}
    \end{figure}

@@

    \appendix

@@

    % \section{Quantum Parameterization of Triangle Structure}
    % \label{sec:param_quantum_dist}
    % \subsection{Unitary Group}
    % \label{sec:unitary_group}
    % To facilitate the parameterization of quantum states states and PVMs, a parameterization of the unitary group of dimension $d$ (denoted $\s{U}\br{d}$) by Spengler, Huber and Hiesmayr~\cite{Spengler_2010_Unitary} is introduced. Discussions of its application to states and measurements are deferred to \cref{sec:states} and \cref{sec:measurements} respectively.

    % In Ref.~\cite{Spengler_2010_Unitary}, Spengler \textit{et al.} proved that all unitaries $U \in \s{U}\br{d}$ can be parameterized without degeneracy as follows:
    % \[ U = \bs{\prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} \exp\br{i P_n \lambda_{n,m}}\exp\br{i \si_{m,n} \lambda_{m,n}}}} \cdot \bs{\prod_{l=1}^{d} \exp\br{iP_l \lambda_{l,l}}}  \eq \label{eq:spengler_unitary_old} \]
    % Where $\la = \bc{\la_{n,m} \mid n,m \in 1, \ldots, d}$ form a $d \times d$ matrix of real-valued parameters with periodicities $\la_{m,n} \in \bs{0, \f{\pi}{2}}$ for $m < n$ and $\la_{m,n} \in \bs{0, 2 \pi}$ for $m \geq n$.
    % \[ \la = \begin{pmatrix}
    %     \la_{1,1} & \cdots & \la_{1, d} \\
    %     \vdots & \ddots & \vdots \\
    %     \la_{d,1} & \cdots & \la_{d, d} \\
    % \end{pmatrix} \]
    % And where $P_l$ are one-dimensional projective operators,
    % \[ P_l = \ket{l}\bra{l} \qquad 1 \leq l \leq d \eq \label{eq:projective_operator} \]
    % and the $\si_{m,n}$ are generalized anti-symmetric $\si$-matrices,
    % \[ \sigma_{m,n} = -i \ket{m}\bra{n} +i \ket{n}\bra{m} \qquad 1 \leq m < n \leq d\]
    % The SSH parameterization (\cref{eq:spengler_unitary}) is unique in that each of the real-valued parameters $\la_{n,m}$ has physical significance. For the sake of reference, let us label the matrix exponential terms in \cref{eq:spengler_unitary} in a manner that corresponds to their affect on an orthonormal basis $\bc{\ket{1}, \ldots, \ket{d}}$.
    % \begin{align*}
    % \begin{split}
    %     GP_l &= \exp\br{iP_l \lambda_{l,l}} \\
    %     RP_{n,m} &= \exp\br{i P_n \lambda_{n,m}} \\
    %     R_{m,n} &= \exp\br{i \si_{m,n} \lambda_{m,n}}
    % \end{split} \eq \label{eq:exp_terms}
    % \end{align*}
    % For example, $R_{m,n} = \exp\br{i \si_{m,n} \lambda_{m,n}}$ applies a rotation to the sub-space spanned by $\ket{m}$ and $\ket{n}$ for $m < n$. Analogously, $RP_{n,m}$ generates the relative phase between $\ket{m}$ and $\ket{n}$ for $m > n$ and $GP_l$ fixes the global phase of $\ket{l}$. Possessing a parameterization that maintains this physical interpretation is useful as it allows one to readily eliminate any degeneracies. For the purposes of quantum distributions such as \cref{eq:quantum_model_triangle}, it should be clear that any contributions to global phase are irrelevant. The SSH parameterization becomes especially attractive because it readily permits one to drop the global phase terms by setting $\la_{l,l} = 0$ for all $l = 1, \ldots, d$. It is convenient to denote the set of all unitaries up to global phase considerations as $\ti {\s{U}}\br{d}$ and express $\ti {U} \in \ti {\s{U}}\br{d}$ using $d\br{d-1}$ real-valued parameters:
    % \[ \ti U = \prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} RP_{n,m}R_{m,n}} \eq \label{eq:spengler_unitary_gp} \]
    % Another attractive feature of the SSH parameterization not mentioned in~\cite{Spengler_2010_Unitary} is that \cref{eq:spengler_unitary}, and thus \cref{eq:spengler_unitary_gp}, can be implemented in a computationally efficient manner. This is discussed in \cref{sec:comp_spengler}.
    % \subsection{Measurements}
    % \label{sec:measurements}
